Probabilistic Policy Violation Detection with IPFWD

### 2017-02-22 paper/main.tex
Revised draft

%  The default action for white-list firewalls is to block all traffic,
%  additional rules describe exceptions. Blacklist firewalls are the opposite,
%  by default they accept all traffic and additional rules describe packet types
%  that are not allowed. Since predicting and blacklisting all possible attacks
%  is not possible in practice, white-list firewall rule sets are the accepted
%  standard and the focus of this paper. Without a security policy,
%  administrators cannot know what to allow and disallow when constructing
%  firewall rules.

    % Packet sampling
    Other papers \cite{exploitingpacketsampling, analysisnetflow,
    monitoringpacketsampling} on packet sampling have been focused on detecting
    and classifying threats, not performance enhancement. However, their
    approaches to packet sampling and the implications addressed provided the
    inspiration for the work done here. The BSD community has produced several in depth investigations into network
    and firewall performance \cite{ipfwvspf,optimizingfreebsd}. Their work
    informed the tests run here.

@@

  IPFWD is a daemon for FreeBSD that updates an early rule in IPFW (the IP
  Firewall) that has a chance to accept any packet. The probability of early
  acceptance is updated over time and dependent on the current system load. In
  high performance systems this can result in an increase in network
  throughput.

>>>>

  Our work uses a form of packet sampling to provide a trade-off between
  complete application of a security policy and increased performance.  Other
  papers \cite{exploitingpacketsampling, analysisnetflow,
  monitoringpacketsampling} on packet sampling have been focused on detecting
  and classifying threats, not performance enhancement. However, their
  approaches to packet sampling and the implications addressed provided the
  inspiration for the work done here. The BSD community has produced several in
  depth investigations into network and firewall performance
  \cite{ipfwvspf,optimizingfreebsd}. Their work informed the tests run here.

@@

  IPFWD is a daemon for FreeBSD that updates an early rule in IPFW (the IP
  Firewall) that has a chance to accept any packet. The probability of early
  acceptance is updated over time and dependent on the current system load. In
  high performance systems this can result in an increase in network
  throughput without additional CPU load.
